---
title: "Coffee quality reviews"
author: "Nasibah Azhari"
date: "10/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The dataset used was scraped from the Coffee Quality Institute website and cleaned
by Reddit user JLD in the Dataset community subreddit. It compiles the reviews
of different coffee products made by professional coffee graders based on 10
attributes.

For more information about the attributes, visit [this page](https://database.coffeeinstitute.org/coffee/976032/grade)

## Loading the libraries

```{r, echo=TRUE, eval=TRUE}
library(tidyverse)
library(ggplot2)
library(munsell)
library(RColorBrewer)
library(Hmisc)
```

## Importing the dataset

```{r}
arabica_coffee <- read_csv("data/arabica_data_cleaned.csv")
```

## Exploring the dataset

```{r}
glimpse(arabica_coffee)
summary(arabica_coffee)
```

## The number of reviewed producers (countries)

```{r}
length(unique(arabica_coffee$Country.of.Origin))
```

## Which countries' products were most frequently reviewed?

```{r}
names(sort(table(arabica_coffee$Country.of.Origin), decreasing = TRUE)[1:10]) -> top_ten_countries
```

I'll focus on the ten most frequently reviewed ones, so the top ten producers were saved in an object to use it to filter by.

## Creating a dataframe with reviews of products from the top ten producers only

```{r}
arabica_coffee %>%
  filter(Country.of.Origin %in% top_ten_countries) -> arabica_coffee_top
```

Using the 'group_by' function, I calculated the mean of each of the 10 attributes:
* Aroma
* Flavour
* Aftertaste
* Acidity
* Body
* Balance
* Uniformity
* Clean Cup
* Sweetness
* Cupper points

```{r}
arabica_coffee_top %>%
  group_by(Country.of.Origin) %>%
  summarise(aroma = mean(Aroma),
            flavour = mean(Flavor),
            aftertaste = mean(Aftertaste),
            acidity = mean(Acidity),
            body = mean(Body),
            balance = mean(Balance),
            unformity = mean(Uniformity),
            clean_cup = mean(Clean.Cup),
            sweetness = mean(Sweetness),
            cupper_points = mean(Cupper.Points)) -> avg_attr
```

## Tidying the dataset..

```{r}
avg_attr %>%
  pivot_longer(-Country.of.Origin,
               names_to = "Attribute",
               values_to = "Rating") -> avg_attr_t
```

## Visualising the dataset

```{r}
posn_j <- position_jitter(0.6)
ggplot(avg_attr_t, aes(x = Attribute, y = Rating, color = Country.of.Origin)) +
  geom_point(position = posn_j) +
  scale_y_continuous(limits = c(0,10)) +
  scale_color_brewer("Country of Origin", type = "qual", palette = "Paired")
```
